Pre-Trained Denoising Autoencoders Long Short-Term Memory Networks as probabilistic Models for Estimation of Distribution Genetic Programming

### 2023-01-10 slides.Rmd
Tue Jan 10 20:00:09 CET 2023: update-remote.sh

```{r full_run_realWorldSymReg_performance, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
library(knitr)
library(kableExtra)

# Create a sample data frame
df <- read.csv("/Users/rmn/github/master_thesis/data/summary_table_final_fit.csv", sep=",")

# Create a function to format the values
bold_min <- function(x, y){
  if(x <= y) return(paste0("**", x, "**"))
  else return(x)
}

# Apply the function to the data frame
df <- mapply(bold_min, df$DAE_GP, df$Pre_Trained_DAE_GP)
#print(df)

fig.pos="H"
knitr::kable(
  df,
  #caption="Performance - Real World Symbolic Regression Benchmark Problems"
)%>% row_spec(0,bold=TRUE ) %>% kableExtra::kable_styling(latex_options = "hold_position", font_size = 7)
```

>>>>

```{r full_run_realWorldSymReg_performance, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
library(knitr)
library(kableExtra)
library(dplyr)

# Create the data frame from csv
df <- read.csv("/Users/rmn/github/master_thesis/data/summary_table_final_fit.csv", sep=",")

# Create a new dataframe with the modified values of the two columns,
df_bold <- df

for(i in 1:nrow(df)){
  if(df[i, "DAE.GP"] < df[i, "Pre.Trained_DAE.GP"])
    df_bold[i, "DAE.GP"] <- sub("^(.*)$", "**\\1**", as.character(df_bold[i, "DAE.GP"]))
  else if (df[i, "DAE.GP"] > df[i, "Pre.Trained_DAE.GP"])
    df_bold[i, "Pre.Trained_DAE.GP"] <- sub("^(.*)$", "**\\1**", as.character(df_bold[i, "Pre.Trained_DAE.GP"]))
}

# 
knitr::kable(
 df_bold,
 format = "markdown",
 digits = 3,
 caption="Performance - Real World Symbolic Regression Benchmark Problems"
)
%>% row_spec(0,bold=FALSE ) %>% kableExtra::kable_styling(latex_options = "hold_position", font_size = 7)
